### 2017-07-27 Paper01_EnthalpyAndCrystallization.tex
Method - turned into sentences

\subsection{Master alloy}
The master alloy of \MgZnCa~ was produced using high-purity elements of Mg (99.85 wt\%), Zn (99.995 wt\%), and Ca (99.8 wt\%). The alloy was prepared by induction melting in boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a circulating Ar atmosphere. Alloy homogeneity was ensured through heating and cooling through a cycle of 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for for injection and gravity casting respectively. Bulk amorphous \MgZnCa~ rod of $2.5 mm$ diameter and plates of thickness of $XX \mu m$ was produced by copper mold injection casting. The $25.4 mm$ diameter targets were prepared from a cylindrical copper mold gravity casting sectioned to thicknesses of $3.25 mm$.

\subsection{\acrshort{dc} magnetron sputtering}
Films were produced from an in-house \acrshort{dc} magnetron sputtering facility with Ar working gas (99.997 vol.\% purity). The power was $15W$, typical voltage of $290-350V$, nominal chamber pressure 1 bar, temperature of 25 \degree C, Ar flow 3.01 \gls{sccm}. Depositions were onto Al substrates for a period of 35 minutes.

\subsection{\acrshort{dsc} characterization}
Isochronic DSC (204 F1 Phoenix, Netzsch, Selb, Germany) was carried out in aluminium crucibles under protective argon atmosphere. Scans were performed at heating rates of 5 to 100 K/min. Film samples were deposited directly into the pan. For annealing XRD samples DSC samples were heated to desired temperature at 20 K/min and then quenched to room temperature before the XRD measurements.

\subsection{\acrshort{xrd} characterization}
Annealing XRD (PANalytical Empyrean) with a Cu $K_{\alpha}$ X-ray source ($\lambda = 1.541 \angstrom$ ). Generator Voltage 45, Tube Current 40, Scan Step Size 0.0262606, Time per step 397.29.

Dynamic XRD (Bruker D8) with a Cu $K_{\alpha}$ X-ray source ($\lambda = 1.541 \angstrom$ ). Generator Voltage 45, Tube Current 100, Scan Step Size 0.02, Time per step 134.4.

The temperature was raised in 5 K increments at 20 K/min. Scans from 31 - 60 2 theta were completed within 1092 seconds (18min 12sec) to minimise the effects of recrystallisation.

>>>>

\subsection{Master alloy}
The master alloy of \MgZnCa~ was produced using high-purity elements of Mg (99.85 wt\%), Zn (99.995 wt\%), and Ca (99.8 wt\%). The alloy was prepared by induction melting in boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a circulating Ar atmosphere. Alloy homogeneity was ensured by heating and cooling through a cycle of 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for for injection and gravity casting respectively. Bulk amorphous \MgZnCa~ rod of $2.5 mm$ diameter and plates of thickness of $XX \mu m$ were produced by copper mold injection casting. The $25.4 mm$ diameter targets were prepared from a cylindrical copper mold gravity castings sectioned to thicknesses of $3.25 mm$. All samples and targets were stored under Ar (99.997 vol.\% purity) when not being examined or used.

\subsection{\acrshort{dc} magnetron sputtering}
Films were produced from an in-house \acrshort{dc} magnetron sputtering facility with Ar working gas (99.997 vol.\% purity). The power was $15W$, typical voltage of $290-350V$, nominal chamber pressure of 1 bar, substrate temperature of 25 \degree C, and Ar flow of 3.01 \acrshort{sccm}. Films were deposited directly onto to Al \acrshort{dsc} lid substrates. Depositions were for a period of 35 minutes. Deposition rate was estimated at $1.2 nm/s$.

\subsection{\acrshort{dsc} characterization}
Isochronic \acrshort{dsc} (204 F1 Phoenix, Netzsch, Selb, Germany) was carried out in aluminium crucibles under a protective Ar (99.997 vol.\% purity) atmosphere. Scans were performed at heating rates of $5$ to $100 K/min$.

For annealed \acrshort{xrd} the samples were heat treated in the \acrshort{dsc} by heating to the desired temperature at $20 K/min$ followed by quenching to room temperature.

\subsection{\acrshort{xrd} characterization}
Annealing \acrshort{xrd} (PANalytical, Empyrean, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed at room temperature. 
(Generator Voltage 45, Tube Current 40, Scan Step Size 0.0262606, Time per Step 397.29).

Dynamic \acrshort{xrd} (Bruker, D8, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed by raising temperature at a rate of $20 K/min$ and performing scans \textit{in situ}. The first scan was performed at 35 \degree C, then 75 \degree C, after which temperature was raised in $5K$ increments. The $2 \theta$ scans from $31 - 60$\degree~ were completed within $1092 sec$ ($18min,~ 12sec$) to minimise the effects of recrystallisation during the experiment. 
(Generator Voltage 45, Tube Current 100, Scan Step Size 0.02, Time per Step 134.4).
